---
title: "p8105_hw1_kx2173"
author: "ke"
date: "9/26/2021"
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```


## Problem 1

Firstly, I create a data frame.

```{r}

# Make sure the randomly generated values are same and reproducible

set.seed(1)

# Create a data frame

pro1_df = tibble(
  vec_num = rnorm(10),
  vec_logical = if_else(vec_num > 0, TRUE, FALSE),
  vec_char = c("First", "Second", "Third", "Forth", "Fifth", "Sixth", "Seventh", "Eighth", "Ninth", "Tenth"),
  vec_factor = factor(c("A", "B", "C", "B", "A", "C", "B", "B", "C", "A"))
)

# Call data frame

pro1_df

```

Then, I extract each variable and calculate means, however, some mean output are "NA"

```{r}

# Extract each variable and calculate means

ext_num = pull(pro1_df, vec_num)
# the mean of the variable "vec_num" is 0.1322028
mean(ext_num)

ext_logical = pull(pro1_df, vec_logical)
# the mean of the variable "vec_logical" is 0.6
mean(ext_logical)

ext_char = pull(pro1_df, vec_char)
# This doesn't work, because this is not a numerical or logical argument
mean(ext_char)

ext_factor = pull(pro1_df, vec_factor)
# This doesn't work, because this is not a numerical or logical argument
mean(ext_factor)

```

In order to fix that, I use as.numeric to convert my logical, character and factor variables, but only logical and factor variables worked.

```{r, eval = FALSE}

# Convert variable to numerical variables and calculate the mean

# all elements are "NA" after converting
num_char = as.numeric(ext_char)

# all elements in ext_factor are converted to "1,2,and 3" after converting
num_factor = as.numeric(ext_factor)
# mean = 2
mean(num_factor)

# converted to "1 and 0", 1 for TRUE and 0 for FALSE
num_logical = as.numeric(ext_logical)
# mean = 0.6
mean(num_logical)

```


## Problem 2

Load the penguin data set

```{r}
data("penguins", package = "palmerpenguins")
```


#### Short description:
the names of variables are: `r names(penguins)`. 
The data set has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.


Finally, we made a scatterplot and save it as a .png file.

```{r}

# Make a scatter plot
plot_df = tibble(
  bill_length = penguins$bill_length_mm,
  flipper_length = penguins$flipper_length_mm,
)

penguins_plot = ggplot(plot_df, aes(x = bill_length, y = flipper_length, color = penguins$species)) + geom_point()

# Save the scatter plot to project directory
ggsave("First scatter plot.png", penguins_plot)

```






